---
title: "Result"
output: html_document
---
Steps of analisys: 
1. Data upload from files

```{r}
testingOrigin <- read.csv("E:/coursera/machineLearning/src/erste/data/pml-testing.csv")
inputDataOrigin <- read.csv("E:/coursera/machineLearning/src/erste/data/pml-training.csv")

```
2. Load packages and set seed

```{r, echo=TRUE,comment=FALSE,message=FALSE}
library(caret);
library(kernlab);
set.seed(32343)
```
3. Preprocessing: remove unnesessary columns
```{r}
drops <- c("cvtd_timestamp", "num_window",
           "raw_timestamp_part_2","raw_timestamp_part_1","X")
inputData<-inputDataOrigin[,!(names(inputDataOrigin) %in% drops)]
testing <- testingOrigin[,!(names(testingOrigin) %in% drops)] 
```
Test data set contains only data with newWindow=no, therefore we will use data with new_window=no only

```{r}
no <- inputData[inputData$new_window %in% c("no"),]
noTest <- testing[testing$new_window %in% c("no"),]
drops <- c("new_window")

no<-no[,!(names(no) %in% drops)]
noTest<-noTest[,!(names(noTest) %in% drops)]
```
Remove empty columns
```{r}
toRemove<-!apply(no, 2, function(x) all(gsub(" ", "", x)=="", na.rm=TRUE))

no <-no[,toRemove]
noTest<-noTest[,toRemove]
```

Divide into test and tain sub sets
```{r}
inTrainNoLess<- createDataPartition(y=no$classe,
                               p=0.7, list=FALSE)
trainingNoT <- no[inTrainNoLess, ]
testingNoT <- no[-inTrainNoLess, ]
```

We will use for prediction random forest algorithm with cross validation with K-fold, K=5, use less trees,than defalt - only 50 
```{r}
controlRf <- trainControl(method="cv", 5)

modFit <- train(classe~ .,data=trainingNoT,method="rf",  trControl=controlRf,ntree=50, prox=TRUE)
```
Make prediction in training and show confusion matrix
```{r}
predictions <- predict(modFit, newdata=testingNoT)
C1 <- confusionMatrix(predictions, testingNoT$classe)
C1
```
Apply trained algorithm to test data and write result into files
```{r}
predictionsTarget <- predict(modFit, newdata=noTest[, -length(names(noTest))])
answers<-predictionsTarget

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(answers)
```


